---
title: "STA304 - Fall 2022"
author: "ADD YOUR NAME HERE - STUDENT NUMBER"
subtitle: Assignment 1
date: "Insert Date Here"
output:
  pdf_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(openintro)
```


# Part 1

### Goal
 
<Explain the goal/topic of your survey here.>

### Procedure

<Explain the goal/topic of your survey here. Also, you should remove the "<>" brackets.>

### Showcasing the survey.

<Provide a link to your survey. Here is an example of how to put a url into your document: [https://www.surveymonkey.co.uk/r/99CGC3B](https://www.surveymonkey.co.uk/r/99CGC3B) [1].>

<Choose 3 questions in your survey to showcase in this submission. It is recommended that you showcase questions of different types (e.g., a combination of numerical and categorical question types). You can format this however you'd like, but we prefer it to be organized. I would recommend bolding the question (using this **Question 1**) and following each question with a description and some commentary on the appropriateness and pros/cons of that particular question.>




\newpage

# Part 2

## Data

<Type here a paragraph introducing the data, its context and the data collection/simulation process.>

```{r, include = FALSE}

# Here you can load in (or simulate) and clean the data (you may need to do the cleaning in a separate R script - this is up to you). 

# You may need additional chunks, in case you want to include some of the cleaning output.

```

<Type here a summary of the cleaning process.>

<Include a description of the important variables.> 

```{r, include=FALSE}

# Use this to calculate some summary measures. 

```


<Include a description of the numerical summaries. Remember you can use `r ` to use inline R code.>




```{r, echo = TRUE}

# Use this to create some plots. 

```

<Include a clear description of the plot(s). I would recommend one paragraph for each plot.> 

All analysis for this report was programmed using `R version 4.0.2`. 


## Methods

<Include some text introducing the methodology.>

<Here you should describe the HT.>

$$ include.your.mathematical.model.here.if.you.have.some.math.to.show $$

<Here you should describe the CI. Here is an example with a citation:>

I will invoke a non-parametric bootstrap [2] to derive the 95\% confidence interval (CI) for the mean age of students in STA304.





## Results 


```{r, include = FALSE}

# Here you can run a your HT/CIs.

# Here you can derive the CIs of interest.


```

<Here you could present your results. You may want to put them into a well formatted table. Be sure that there is some text describing the results.>


<Note: Alternatively you can use the `knitr::kable` function to create a well formatted table from your code. See here: [https://rmarkdown.rstudio.com/lesson-7.html](https://rmarkdown.rstudio.com/lesson-7.html). If you do this, be sure to include this in the bibliography [3].>



## Bibliography

1. Grolemund, G. (2014, July 16) *Introduction to R Markdown*. RStudio. [https://rmarkdown.rstudio.com/articles_intro.html](https://rmarkdown.rstudio.com/articles_intro.html). (Last Accessed: May 5, 2021) 

2. Dekking, F. M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

3.  Allaire, J.J., et. el. *References: Introduction to R Markdown*. RStudio. [https://rmarkdown.rstudio.com/docs/](https://rmarkdown.rstudio.com/docs/). (Last Accessed: May 5, 2021) 




\newpage

## Appendix


Here is a glimpse of the data set simulated/surveyed:

```{r, echo = FALSE}

# glimpse(my_data)

```




