---
title: "A2 Eric"
output: html_document
date: "2022-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load libraries 

```{r}
library(tidyverse)
library(mgcv)
library(xgboost)
library(missForest)
library(doParallel)
library(cesR)
library(caret)
library(randomForest)
library(GGally)
library(forcats)
library(purrr)

registerDoParallel(cores=24)
```

# load in finished datasets 

```{r}
set.seed(123)
predictors_all <- read_csv("ces2019_web_all_predictors.csv") %>% mutate_if(is.character, as.factor) %>% select(-c(income_number)) %>% mutate(vote_choice = as.factor(vote_choice)) %>% as.data.frame()
predictors_reduced <- read_csv("ces2019_web_reduced_predictors.csv") %>% mutate_if(is.character, as.factor) %>% mutate(vote_choice = as.factor(vote_choice)) %>% as.data.frame()

train_full <- predictors_all %>% sample_frac(0.8)
test_full <- predictors_all %>% anti_join(train_full, by = "cps19_ResponseId")

train_full <- train_full %>% select(-c(cps19_ResponseId))
test_full <- test_full %>% select(-c(cps19_ResponseId))


train_reduced <- predictors_reduced %>% sample_frac(0.8)
test_reduced <- predictors_reduced %>% anti_join(train_reduced, by = "cps19_ResponseId")

train_reduced <- train_reduced %>% select(-c(cps19_ResponseId))
test_reduced <- test_reduced %>% select(-c(cps19_ResponseId))

glimpse(train_full)
glimpse(train_reduced)
```

# data exploration 

## perform feature selection 
```{r}
set.seed(123)
# use recursive feature selection 
predictors <- train_full %>% select(-c(vote_choice))
output <- train_full %>% select(vote_choice)
rfe_control <- rfeControl(
                      functions = rfFuncs,
                      method = "repeatedcv",
                      repeats = 5,
                      number = 5)
rfe_predictors <- rfe(x = predictors[, 1:ncol(predictors)], y = output[, 1], sizes = c(1:ncol(predictors)), rfeControl = rfe_control)
save(rfe_predictors, file = "rfe_predictors.RData")
```

```{r}
rfe_predictors
predictors(rfe_predictors)
```

# model tests

```{r}
library(GGally)
ggpairs(predictors_full_no_na %>% select(c(liberal_favour, conservative_favour, ndp_favour, bloc_favour, green_favour, vote_choice)))
```

## GAM full model

```{r}
library(parallel)
train_full <- train_full %>% mutate(vote_choice = as.numeric(as.character(vote_choice)))
test_full <- test_full %>% mutate(vote_choice = as.numeric(as.character(vote_choice)))


test_gam <- mgcv::gam(list(vote_choice ~ s(liberal_favour), 
                           ~ s(liberal_favour), 
                           ~ s(liberal_favour),
                           ~ s(liberal_favour),
                           ~ s(liberal_favour)),
                      data = train_full, 
                      family = multinom(K=5), 
                      method = "REML",
                      control = mgcv::gam.control(nthreads= 24))


ran_effects.full <- mgcv::gam(data = train_full, formula = 
                         list(
                           vote_choice ~ s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"), 
                           ~ s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"), 
                           ~ s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "fs") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"),
                           ~ s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"),
                           ~ s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re")
                        ), 
                       family = mgcv::multinom(K=5),  
                       method="REML")
summary(ran_effects_gam_model)

plot(ran_effects.full, pages = 1, trans = plogis,
     shift = coef(ran_effects.full)[1], seWithMean = TRUE)
```

```{r}
# mixed effects model
mixed_effects.full <- mgcv::gam(data = train_full, 
                                         formula = list(
                                           vote_choice ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs="re") + s(health, bs = "re") +s(age_category, bs = "re") + s(education, bs = "re") + s(income_category, bs="re") + s(marital_status, bs = "re") + s(language, bs = "re") + s(gender, bs = "re") + s(owns_house, bs = "re") + s(born_in_canada, bs = "re") + s(citizenship, bs="re")
                                         ), 
                                         family = mgcv::multinom(K=5), 
                                         method = "REML")
```

```{r}
# fixed effects model
fixed_effects.full <- mgcv::gam(data = train_full, 
                                         formula = list(
                                           vote_choice ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") ,
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps")
                                         ), 
                                         family = mgcv::multinom(K=5))
```


## Reduced Complexity Model 

```{r}
train_reduced <- train_reduced %>% mutate(vote_choice = as.numeric(as.character(vote_choice)))
test_reduced <- test_reduced %>% mutate(vote_choice = as.numeric(as.character(vote_choice)))

# random effects only 
ran_effects.reduced <- mgcv::gam(data = train_reduced, formula = 
                         list(
                           vote_choice ~ s(province, bs="re") + s(language, bs = "re"), 
                           ~ s(province, bs="re") + s(language, bs = "re"), 
                           ~ s(province, bs="re") + s(language, bs = "re"),
                           ~ s(province, bs="re") + s(language, bs = "re"),
                           ~ s(province, bs="re") + s(language, bs = "re")
                        ), 
                       family = mgcv::multinom(K=5),  
                       method="REML")
summary(ran_effects_gam_model)

plot(ran_effects.reduced, pages = 1, trans = plogis,
     shift = coef(ran_effects.reduced)[1], seWithMean = TRUE)

# mixed effects model
mixed_effects.reduced <- mgcv::gam(data = train_reduced, 
                                         formula = list(
                                           vote_choice ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs = "re") + s(language, bs = "re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs = "re") + s(language, bs = "re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs = "re") + s(language, bs = "re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs = "re") + s(language, bs = "re"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") + s(province, bs = "re") + s(language, bs = "re")
                                         ), 
                                         family = mgcv::multinom(K=5), 
                                         method = "REML")
# fixed effects model
fixed_effects.reduced <- mgcv::gam(data = train_reduced, 
                                         formula = list(
                                           vote_choice ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps") ,
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps"),
                                           ~ s(liberal_favour, bs="ps") + s(conservative_favour, bs="ps") + s(ndp_favour, bs="ps") + s(green_favour, bs="ps") + s(people_favour, bs="ps") + s(bloc_favour, bs="ps")
                                         ), 
                                         family = mgcv::multinom(K=5))
```




## evaluate model performance 

### reduced models

```{r}
ran_effects.reduced.predictions <- predict(ran_effects.reduced, type="response", newdata = test_reduced)
mixed_effects.reduced.predictions <- predict(mixed_effects.reduced, type="response", newdata = test_reduced)
fixed_effects.reduced.predictions <- predict(fixed_effects.reduced, type="response", newdata = test_reduced)
```

```{r}
ran_effects.reduced.confusion <- confusionMatrix(data = ran_effects.reduced.predictions, reference = test_reduced$vote_choice)
mixed_effects.reduced.confusion <- confusionMatrix(data = mixed_effects.reduced.predictions, reference = test_reduced$vote_choice)
fixed_effects.reduced.confusion <- confusionMatrix(data = fixed_effects.reduced.predictions, reference = test_reduced$vote_choice)
```


### full model

```{r}
ran_effects.full.predictions <- predict(ran_effects.full, type="response", newdata = test_full)
mixed_effects.full.predictions <- predict(mixed_effects.full, type="response", newdata = test_full)
fixed_effects.full.predictions <- predict(fixed_effects.full, type="response", newdata = test_full)
```

### save model predictions 

```{r}
ran_effects.full.predictions <- as.data.frame(ran_effects.full.predictions)
colnames(ran_effects.full.predictions) <-  c("ran_effects.lib_prob",  "ran_effects.con_prob", "ran_effects.ndp_prob", "ran_effects.blc_prob", "ran_effects.grn_prob", "ran_effects.ppl_prob")

mixed_effects.full.predictions <- as.data.frame(mixed_effects.full.predictions)
colnames(mixed_effects.full.predictions) <- c("mixed_effects.lib_prob",  "mixed_effects.con_prob", "mixed_effects.ndp_prob", "mixed_effects.blc_prob", "mixed_effects.grn_prob", "mixed_effects.ppl_prob")

fixed_effects.full.predictions <- as.data.frame(fixed_effects.full.predictions)
colnames(fixed_effects.full.predictions) <- c("fixed_effects.lib_prob",  "fixed_effects.con_prob", "fixed_effects.ndp_prob", "fixed_effects.blc_prob", "fixed_effects.grn_prob", "fixed_effects.ppl_prob")

full_predictions_df <- cbind(test_full, ran_effects.full.predictions, mixed_effects.full.predictions, fixed_effects.full.predictions) 
full_predictions_df %>% write_csv("full_model_predictions.csv")
```

```{r}
ran_effects.reduced.predictions <- as.data.frame(ran_effects.reduced.predictions)
colnames(ran_effects.reduced.predictions) <-  c("ran_effects.lib_prob",  "ran_effects.con_prob", "ran_effects.ndp_prob", "ran_effects.blc_prob", "ran_effects.grn_prob", "ran_effects.ppl_prob")

mixed_effects.reduced.predictions <- as.data.frame(mixed_effects.reduced.predictions)
colnames(mixed_effects.reduced.predictions) <- c("mixed_effects.lib_prob",  "mixed_effects.con_prob", "mixed_effects.ndp_prob", "mixed_effects.blc_prob", "mixed_effects.grn_prob", "mixed_effects.ppl_prob")

fixed_effects.reduced.predictions <- as.data.frame(fixed_effects.reduced.predictions)
colnames(fixed_effects.reduced.predictions) <- c("fixed_effects.lib_prob",  "fixed_effects.con_prob", "fixed_effects.ndp_prob", "fixed_effects.blc_prob", "fixed_effects.grn_prob", "fixed_effects.ppl_prob")

reduced_predictions_df <- cbind(test_reduced, ran_effects.reduced.predictions, mixed_effects.reduced.predictions, fixed_effects.reduced.predictions) 
reduced_predictions_df %>% write_csv("reduced_model_predictions.csv")
```

### compute eval metrics 

```{r}
# true values from test set - provincal voting 
provincal_ground_truth <- test_full %>% group_by(province) %>% mutate(province_popn = n()) %>% ungroup() 
provincal_ground_truth <- provincal_ground_truth %>% group_by(province, vote_choice) %>% summarize(provincal_proportions = n()/province_popn) %>% unique()
provincal_vote_choices <- provincal_ground_truth %>% group_by(province)
provincal_vote_choice <- provincal_vote_choices %>% slice_max(provincal_proportions) %>% select(vote_choice) %>% mutate(provincal_vote_choice = vote_choice) %>% select(-c(vote_choice))
provincal_ground_truth <- provincal_ground_truth %>% ungroup() %>% mutate(individual_vote_choice = vote_choice) %>% select(-c(vote_choice)) %>% left_join(provincal_vote_choice, by = "province")
provincal_ground_truth
provincal_vote_choices
provincal_vote_choice 
write_csv(provincal_vote_choices, "provincal_vote_proportions.csv")
write_csv(provincal_vote_choice, "provincal_vote_choice.csv")
```

```{r}
# true values from test set - national aggregate 
national_ground_truth <- test_full %>% mutate(national_popn = n()) %>% ungroup() 
national_ground_truth <- national_ground_truth %>% group_by(vote_choice) %>% summarize(national_proportions = n()/national_popn) %>% unique()
national_vote_choices <- national_ground_truth
national_vote_choice <- national_vote_choices %>% ungroup %>% slice_max(national_proportions) 
national_vote_choice
national_vote_choices
write_csv(national_vote_choices, "national_vote_choices.csv")
```

#### perform post stratification 

```{r}
full_predictions_df <- full_predictions_df %>% mutate(province = fct_recode(province, "Manitoba" = "Maintoba", "Nova Scotia" = "Nova Scoita")) %>% mutate_if(is.factor, as.character)
reduced_predictions_df <- reduced_predictions_df %>% mutate(province = fct_recode(province, "Manitoba" = "Maintoba" , "Nova Scotia" = "Nova Scoita")) %>% mutate_if(is.factor, as.character)
# load population datasets 
census_reduced <- read_csv("gss_poststrat_weights_reduced.csv") 
census_full <- read_csv("gss_poststrat_weights_all.csv") 

glimpse(census_full)
glimpse(test_full)
```


Post-stratification for the national level
$$ 
\hat{y}^{ps} = \frac{\sum_{j=1}^{J}N_j \cdot \hat{y}_j}{\sum_{j=1}^{J}N_j} 
$$

```{r}
poststrat.full.combined_national_df <- census_full %>% 
  right_join(full_predictions_df) %>% 
  mutate_if(is.character, as.factor) %>% 
  select(matches("*_prob")) %>% 
  unique() %>% # can't do this; not enough post stratification cells 
  summarize(across(everything(), mean))
poststrat.full.combined_national_df

write_csv(poststrat.full.combined_national_df, "full.national_preds.csv")

poststrat.reduced.combined_national_df <- census_reduced %>% 
  right_join(reduced_predictions_df) %>%
  drop_na() %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(across(ran_effects.lib_prob:fixed_effects.ppl_prob, ~ category_samples * .x))

poststrat.reduced.national_preds <- poststrat.reduced.combined_national_df %>% 
  select(matches("*_prob"), total_samples) %>% 
  mutate(across(ran_effects.lib_prob:fixed_effects.ppl_prob, ~ .x / total_samples)) %>% 
  select(-c(total_samples)) %>% 
  unique() %>% 
  summarize(across(everything(), sum))
poststrat.reduced.national_preds
write_csv(poststrat.reduced.national_preds, "poststrat.reduced.national_preds.csv")
```

Post-stratification for province level 
$$ 
\hat{y}^{ps}_{\text{Province}} = \frac{\sum_{j\in J_s}N_j \cdot \hat{y}_j}{\sum_{j\in J_s}N_j} 
$$

```{r}
poststrat.full.combined_provincal_df <- census_full %>% 
  right_join(full_predictions_df) %>% 
  group_by(province) %>%
  mutate_if(is.character, as.factor) %>% 
  select(matches("*_prob")) %>% 
  unique() %>% # can't do this; not enough post stratification cells 
  summarize(across(everything(), mean))

poststrat.full.combined_provincal_df

write_csv(poststrat.full.combined_provincal_df, "poststrat.full.provincal_preds.csv")

poststrat.reduced.combined_provincal_df <- census_reduced %>% 
  right_join(reduced_predictions_df) %>% mutate_if(is.character, as.factor) %>% 
  group_by(province) %>% 
  mutate(total_samples = n()) %>% 
  ungroup() %>% 
  group_by(province, language) %>% 
  mutate(category_samples = n()) %>% 
  mutate(poststrat_weight = category_samples/total_samples) %>% 
  ungroup() %>% 
  group_by(province) %>% 
  mutate(across(ran_effects.lib_prob:fixed_effects.ppl_prob, ~ category_samples * .x))

poststrat.reduced.provincal_preds <- poststrat.reduced.combined_provincal_df %>% 
  select(matches("*_prob"), total_samples) %>% 
  mutate(across(ran_effects.lib_prob:fixed_effects.ppl_prob, ~ .x / total_samples)) %>% 
  select(-c(total_samples)) %>% 
  unique() %>% 
  summarize(across(everything(), sum))
poststrat.reduced.provincal_preds

write_csv(poststrat.reduced.provincal_preds, "poststrat.reduced.provincal_preds.csv")

poststrat.reduced.provincial_pred.ran <- poststrat.reduced.provincal_preds %>% 
  select(province, matches("ran_effects*")) %>% 
  mutate(vote_choice = pmap_chr(select(., ran_effects.lib_prob:ran_effects.ppl_prob), 
                                ~ c(...) %>% 
                                   which.max %>% 
                                   names )) %>% 
  mutate(vote_choice = case_when( 
      vote_choice == "ran_effects.lib_prob" ~ "Liberal Party", 
      vote_choice == "ran_effects.con_prob" ~ "Conservative Party", 
      vote_choice == "ran_effects.ndp_prob" ~ "New Democratic Party", 
      vote_choice == "ran_effects.blc_prob" ~ "Bloc Québécois", 
      vote_choice == "ran_effects.grn_prob" ~ "Green Party", 
      vote_choice == "ran_effects.ppl_prob" ~ "People's Party"
    )) %>% 
  select(province, vote_choice)

poststrat.reduced.provincial_pred.mixed <- poststrat.reduced.provincal_preds %>% 
  select(province, matches("mixed_effects*")) %>% 
  mutate(vote_choice = pmap_chr(select(., mixed_effects.lib_prob:mixed_effects.ppl_prob), 
                                ~ c(...) %>% 
                                   which.max %>% 
                                   names )) %>% 
  mutate(vote_choice = case_when( 
      vote_choice == "mixed_effects.lib_prob" ~ "Liberal Party", 
      vote_choice == "mixed_effects.con_prob" ~ "Conservative Party", 
      vote_choice == "mixed_effects.ndp_prob" ~ "New Democratic Party", 
      vote_choice == "mixed_effects.blc_prob" ~ "Bloc Québécois", 
      vote_choice == "mixed_effects.grn_prob" ~ "Green Party", 
      vote_choice == "mixed_effects.ppl_prob" ~ "People's Party"
    )) %>% 
  select(province, vote_choice)

poststrat.reduced.provincial_pred.fixed <- poststrat.reduced.provincal_preds %>% 
  select(province, matches("fixed_effects*")) %>% 
  mutate(vote_choice = pmap_chr(
    select(., fixed_effects.lib_prob:fixed_effects.ppl_prob), 
          ~ c(...) %>% 
             which.max %>% 
             names )) %>% 
  mutate(vote_choice = case_when( 
      vote_choice == "fixed_effects.lib_prob" ~ "Liberal Party", 
      vote_choice == "fixed_effects.con_prob" ~ "Conservative Party", 
      vote_choice == "fixed_effects.ndp_prob" ~ "New Democratic Party", 
      vote_choice == "fixed_effects.blc_prob" ~ "Bloc Québécois", 
      vote_choice == "fixed_effects.grn_prob" ~ "Green Party", 
      vote_choice == "fixed_effects.ppl_prob" ~ "People's Party"
    )) %>% 
  select(province, vote_choice)
```


## save all models 
```{r}
save(fixed_effects.reduced, mixed_effects.reduced, ran_effects.reduced, file = "reduced_models.RData")
save(fixed_effects.full, mixed_effects.full, ran_effects.full, file = "full_models.RData")
```

## load all models 


```{r}
load("reduced_models.RData")
load("full_models.RData")
```